---
title: "Class Dashboard Example"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(rcartocolor)
library(plotly)
```

About {.sidebar}
============
## About
Your text here. You can use markdown syntax, including [links](http://blah.com), *italics*, **bolding**, etc.

# Car stuff {data-icon="fa-car"}

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r plot1}

p <- ggplot(mtcars, aes(mpg, disp)) +
  geom_point(aes(color = wt)) +
  #geom_smooth(color = "gray70") +
  theme_minimal() +
  scale_color_viridis_c()

ggplotly(p)

```

Column {data-width=350, .tabset}
-----------------------------------------------------------------------

### Chart B

```{r plot2}

ggplot(mtcars, aes(gear, hp, fill = wt)) +
   geom_col(width = 0.60, 
            alpha = 0.6) +
   scale_fill_carto_c(palette = "Burg") +
   theme_minimal()

```

> Here's a fancy bar graph showing the relation between the number of gears and horse power, colored by vehicle weight. hahdaihdioahdiahdioa hioahdoisah haodihsaiodaiohdaio hadiaoihdiaoh dhaihdiash dahihdaioh ah dahoihd anadihdiaoh d ahidha blah blah blah.

### Chart C

```{r plot3}

ggplot(mpg, aes(displ, cty)) +
  geom_point(aes(color = drv)) +
  geom_smooth() +
  theme_minimal()

```

# Other stuff {data-icon="fa-university"}

Column {data-width=650}
-----------------------------------------------------------------------

```{r plot4}


```

